Ms. No. PSRM-OA-2019-0126.R1 entitled ``Taking Dyads Seriously''

### 2021-01-08 revisionMemo2/rev1.tex
rev 1

		We thank the reviewer for taking the time to provide their comments and helping us to make the manuscript more focused. We have made a number of changes to the framing of the article per the reviewer's suggestions.

@@

		something, something.

@@

		speaking specifically about glms so ...

>>>>

		We thank the reviewer for taking the time to provide their comments and helping us to make the manuscript more focused. We have made a number of changes to the framing of the article per the reviewer's suggestions, these appear throughout the manuscript, but especially on pages X.

@@

		Thank you for the suggestion, we have made this change on page X.

@@

		We understand the position that a detailed discussion of specifying a likelihood under iid seems laborious and potentially unnecessary. After a lengthy discussion among our co-authors, we have decided to retain this section of the paper. We believe that since our approach is directly aimed at applied scholarship in International Relations, and because we focus on applications that have appeared in top journals during the last 10 years, this section enables our study to serve a broad audience of readers. By keeping it, we ensure that a reader can directly follow our main points about GLM specifications and how the AME addresses these concerns. 
